COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
knitting successful & pretty :) thanks Christoph

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : no
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}

@@

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  #library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package

@@

@@

@@

@@

@@

  #create table
  h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
                             round(m1_h2c.ss$slopes[c(2:3)], digits = 2),
                             c(paste0("[", round(m1_h2c.ss$slopes[1,4], digits = 2), ",", round(m1_h2c.ss$slopes[1,5], digits = 2), "]"),
                               paste0("[", round(m1_h2c.ss$slopes[2,4], digits = 2), ",", round(m1_h2c.ss$slopes[2,5], digits = 2), "]"),
                               paste0("[", round(m1_h2c.ss$slopes[3,4], digits = 2), ",", round(m1_h2c.ss$slopes[3,5], digits = 2), "]")),
                             round(m1_h2c.ss$slopes[7], digits = 3),
                             round(m1_h2c.ss$ints[c(2,3)], digits = 2))
  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI", "$p$-value", "Beta", "$SE$" )
  # columns 2:5 belong to "Slopes of NFC"
  # columns 6:7 belong to "Conditional Intercept"

@@

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
    geom_line(aes(group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign)) +
    geom_text(x = 3, y = -0.01, label = "NFC") +
    geom_text(x = 3, y = -0.12, label = "Level") +
    theme_classic() +
    labs(x = NULL, y = "Fixed effects estimate \u03b2") +
    scale_y_continuous(lim = c(NA,0.01)) +
    theme(axis.text.x = element_blank(),
          axis.line.y = element_line(size = 1, color = "black"), axis.title.y = element_text(margin = margin(r = 10)),
          legend.position = "none")

@@

### Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1a XXX"
  , note = "XXX."
  , escape = TRUE
)
```

### Hypothesis 1b: Reaction time increases with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1b XXX"
  , note = "XXX."
  , escape = TRUE
)
```

### Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_physical_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_performance_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_effort_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_frustration_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
  , note = "XXX."
  , escape = TRUE
)
```

### Hypothesis 2a: Subjective values decline with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis2a_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
  , note = "XXX."
  , escape = TRUE
)
```

### Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.

@@

### Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  h2c_ss.table
  , caption = "Simple slope analysis of SVs...XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = TRUE, point.shape = TRUE,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = TRUE) + theme_apa() +
scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
```
Johnson-Neyman intervals:

@@

```{r Fig2cSA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity."}

@@

  ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
```

### Hypothesis 3a: Subjective values positively predict individual NCS scores.

@@

### Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.

>>>>

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}

@@

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}

  knitr::opts_chunk$set(out.width = "\\textwidth")
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  #library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package

@@

  # rename columns and contrasts for apa_print

  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)

@@

  # rename columns and contrasts for apa_print

  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)

@@

  # rename columns and contrasts for apa_print

  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)

@@

  # rename columns and contrasts for apa_print

  colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis2a_contrasts$Contrast <- gsub("X", "", hypothesis2a_contrasts$Contrast)

@@

  #create table
  h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
                             round(m1_h2c.ss$slopes[c(2:3)], digits = 2),
                             c(paste0("[", round(m1_h2c.ss$slopes[1,4], digits = 2), ",", round(m1_h2c.ss$slopes[1,5], digits = 2), "]"),
                               paste0("[", round(m1_h2c.ss$slopes[2,4], digits = 2), ",", round(m1_h2c.ss$slopes[2,5], digits = 2), "]"),
                               paste0("[", round(m1_h2c.ss$slopes[3,4], digits = 2), ",", round(m1_h2c.ss$slopes[3,5], digits = 2), "]")),
                             round(m1_h2c.ss$slopes[7], digits = 3),
                             round(m1_h2c.ss$ints[c(2,3)], digits = 2))
  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95\\% CI", "$p$-value", "Beta", "$SE$" )
  # columns 2:5 belong to "Slopes of NFC"
  # columns 6:7 belong to "Conditional Intercept"

@@

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
    geom_line(aes(group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign)) +
    geom_text(x = 3, y = -0.01, label = "NFC") +
    geom_text(x = 3, y = -0.12, label = "Level") +
    theme_classic() +
    labs(x = NULL, y = "Fixed effects\nestimate \u03b2") +
    scale_y_continuous(lim = c(NA,0.01)) +
    theme(axis.text.x = element_blank(),
          axis.line.y = element_line(size = 1, color = "black"), axis.title.y = element_text(margin = margin(r = 10)),
          legend.position = "none")

@@

## Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

## Hypothesis 1b: Reaction time increases with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_physical_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_performance_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_effort_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_frustration_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

## Hypothesis 2a: Subjective values decline with increasing n-back level.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis2a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing subjective values between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

## Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.

@@

## Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.

@@

`r table_2`

@@

interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = TRUE, point.shape = TRUE,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = TRUE) + theme_apa() +
scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
```

Johnson-Neyman intervals:

@@

```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity."}

@@

  ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))

## Hypothesis 3a: Subjective values positively predict individual NCS scores.

@@

## Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.
